---
title: "Project"
author: "Tendai Makuwerere , Mark Asamoah , Sandile Nhlalo-Sibanda "
date: "5/29/2022"
output: 
  html_document:
    number_sections: true
    toc_float: true
    toc: true
    toc_depth: 4
    theme: united
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(ggthemes))
suppressPackageStartupMessages(library(plotly))
suppressPackageStartupMessages(library(dplyr))
```

## Importing the original dataset

```{r}
df <- read.csv2('https://raw.githubusercontent.com/mcasky16/RR_Final_Project/main/student_feedback.csv', sep = ',')
```


COLUMN NAMES

names(df)
##  [1] "X"                                                   
##  [2] "Student.ID"                                          
##  [3] "Well.versed.with.the.subject"                        
##  [4] "Explains.concepts.in.an.understandable.way"          
##  [5] "Use.of.presentations"                                
##  [6] "Degree.of.difficulty.of.assignments"                 
##  [7] "Solves.doubts.willingly"                             
##  [8] "Structuring.of.the.course"                           
##  [9] "Provides.support.for.students.going.above.and.beyond"
## [10] "Course.recommendation.based.on.relevance"

POTENTIAL QUESTIONS TO BE ANSWERED
How is “course recommendation based on relevance distributed” as density plot?

Average use of presentation

CORRELATION between solves doubt AND explain concept in an understandable way

Bar chart student well versed with the topic

on the scale to one to 10 how much difficult assignment is 6- scale and 7-scale

Bar chart rating for teacher that Solves doubt willingly

REMOVING MISSING VALUES TO CLEAN THE DATA AND AVOID ERRORS

df_nona implies df with no null values

```{r}
df_nona = df%>%drop_na()
```

How is “course recommendation based on relevance distributed” as density plot?

```{r pressure, echo=FALSE}
ggplot(df_nona , aes(x=Course.recommendation.based.on.relevance)) + 
  geom_density(bins=1, color="black", fill="orange",
               linetype="dashed")+
  labs(title = 'Course.recommendation.based.on.relevance',
       subtitle= 'Mumbai student feedback' , x= 'Course.recommendation.based.on.relevance',y= 'Frequency') +
  ggthemes::theme_solarized_2()
```


## Average use of presentation

```{r}
df_nona %>%
summarize(average_use_ofpresentation= round(mean(Use.of.presentations)))
```
##   average_use_ofpresentation
## 1                          6
on the scale of 1-10 average ratimg that student feel that they will use presentation for topic is 6

on the scale to one to 10 ho much difficult assignment is 6- scale and 7-scale

```{r}
df_nona %>%
  filter(Degree.of.difficulty.of.assignments %in% c('6', '7'))%>%
  ggplot() + 
  geom_density(aes(x = Degree.of.difficulty.of.assignments , fill = Degree.of.difficulty.of.assignments , alpha = 0.1))+
  labs(title = 'Degree.of.difficulty.of.assignments',
       subtitle= 'Mumbai student survey' , x= 'Degree.of.difficulty.of.assignments',y= 'Frequency') +
  ggthemes::theme_stata()
```

## Bar chart student well versed with the topic

```{r warning=FALSE}
df_nona %>%
  group_by(Well.versed.with.the.subject)%>%
  count(sort =TRUE) %>%
  head(10)%>%
  ggplot() +
  geom_col(aes(x= reorder(Well.versed.with.the.subject , n) , y = n), fill = "Pink")  + 
  geom_label(aes(x= reorder(Well.versed.with.the.subject , n) , y = n , label=n))+
  coord_flip() +
  labs(title = 'no. of student who are well versed ',
        x= 'scale',y= 'Frequency')+
  ggthemes::theme_economist_white()-> scale.... 
plotly:: ggplotly(scale....)
```


## Bar chart rating for teacher that Solves doubt willingly

```{r warning=FALSE}
df_nona %>%
  group_by(Solves.doubts.willingly)%>%
  count(sort =TRUE)%>%
  ggplot() +
  geom_col(aes(x= reorder(Solves.doubts.willingly, n) , y = n), fill = "purple" )  + 
  geom_label(aes(x= reorder(Solves.doubts.willingly , n) , y = n , label=n))+
 
  ggthemes::theme_gdocs()->gg....Solves.doubts.willingly
plotly:: ggplotly(gg....Solves.doubts.willingly)
```

## CORRELATION BETWEEN solves doubt AND explain concept in an understandable way

```{r warning=FALSE}
df_nona%>%
  select(c('Solves.doubts.willingly' ,'Explains.concepts.in.an.understandable.way')) %>%
  cor()

```
correlation less than 0  indicate a negative correlation in our case it is -0.0258 

## SCATTER PLOT  
Since the points or values are range in absolute integer the scatter plot is not showing good result
```{r message=FALSE, warning=FALSE}
df_nona%>%
  select(c('Solves.doubts.willingly' ,'Explains.concepts.in.an.understandable.way')) %>%
  ggplot(aes(x= Solves.doubts.willingly , y = Explains.concepts.in.an.understandable.way))+
  geom_point(color = "#6c094f")+
  geom_smooth(method = lm)+
  labs(title = "correlation Scatter Plot" )

```

## Importing the Survey dataset

```{r}
df <- read.csv2('https://raw.githubusercontent.com/mcasky16/RR_Final_Project/main/RR_survey.csv', sep = ',')
```